---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ussie

<!-- badges: start -->
[![R-CMD-check](https://github.com/kathy-nevola/ussie/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kathy-nevola/ussie/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/kathy-nevola/ussie/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/kathy-nevola/ussie/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of ussie is to clean and analyze data from the engsoccerdata package (Curley 2016). This is a demo package that was made as part of the 2022 RStudio Conference, during the Building Tidy Tools workshop.

## Installation

You can install the development version of ussie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kathy-nevola/ussie")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ussie)
library(engsoccerdata)
england<-uss_make_matches(engsoccerdata::england, "England")
head(england)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
